Landscape heterogeneity simulation figures

### 2018-04-09 Manuscript_figures_2017_12_12.Rmd
Updated figure order and commented code

---
title: "Landscape heterogeneity simulation figures"
author: "Lauren White"
date: "December 12, 2017"
output: html_document
---

## Load packages
```{r}
library(doBy)
library(ggplot2)
library(viridis)
library(ggthemes)
library(scales)
library(lsr)
library(SDMTools)
```

## Load and update summary dataset

```{r}
#Set working directory to where IBMsummary.csv is located
#setwd()
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

@@

#Set working directory of where to produce Figures
#setwd()
```

@@

## Figure 1
Representation of neutral landscapes
```{r}
#' Create neutral landscape maps
library(raster)

>>>>

---
title: "Landscape heterogeneity simulation figures"
author: "Lauren White"
date: "April 3, 2018"
output: html_document
---

## Load packages
```{r}
library(doBy)
library(ggplot2)
library(viridis)
library(ggthemes)
library(scales)
library(lsr)
library(SDMTools)
library(cowplot)
```

## Load and update summary dataset
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

@@

#Set working directory of where to produce Figures
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
```

@@

##Figure 1
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab("")+
    theme_bw()+
    ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8)) +
    theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))+
    coord_flip()
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
B<-ggplot(imp_logitprev, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab("")+
    theme_bw()+
    ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8)) +
    theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))+
    coord_flip()
B

#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
C<-ggplot(imp_logitdur, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
    ylab("Mean Decrease in Accuracy (%IncMSE)") +
    theme_bw()+
    ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +

      theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title.x=element_text(size=7)) +
    theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))+
    coord_flip()
C

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("Figure1_RF.tiff", height =10 , width =8.7, units = "cm", compression = "lzw", res = 1200)
multiplot(A, B, C, cols=1)
dev.off()

##Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy (%IncMSE)") +
    #ylab("")+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
B<-ggplot(imp_logitprev, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.25, 0, 0, 0), "cm"))+
    #ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8))
    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
    #coord_flip()
B

#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
C<-ggplot(imp_logitdur, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
    #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +

      theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title.x=element_text(size=7)) 
    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
    #coord_flip()
C

prow <- plot_grid(A, B, C,
           align = 'vh',
           labels = c("(A)", "(B)", "(C)"),
           hjust = -0.75,
           ncol = 3, label_size=7
           )
#paxis <- axis_canvas(prow, axis = "y") 
#ggdraw(insert_yaxis_grob(prow, paxis, grid::unit(.25, "null")))

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

##Figure 2
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)

#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
gg<- ggplot(data=sub_data, aes(y=max_prevalence, x=as.factor(rec_rate)))
#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
gg<-gg+ geom_boxplot()+ facet_grid(r ~ d, scales= "free_x", labeller=label_value)
gg<- gg+ labs(x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence") #,title="(A)")
#gg<- gg+ theme(axis.title.x = element_text(face="bold", size=10),title=element_text(face="bold", size=10))
gg<- gg + theme(axis.text = element_text(size=6))
gg<- gg + theme(axis.text.x =element_text(vjust= 0, angle=-90))
gg<- gg + theme(axis.title = element_text(vjust=0.5, size=7))
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=6))
gg<- gg + theme(plot.title = element_text(size = 7))
gg<- gg + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
#gg<-gg + geom_text(data = means , aes(label = duration, y = duration + 0.08))

gg
#dev.off()

#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
hh<- ggplot(data=sub_data, aes(x=as.factor(rec_rate), y=duration))
#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
hh<-hh+ geom_boxplot()+ facet_grid(r ~ d, scales= "free_x", labeller=label_value)
hh<- hh+ labs(fill= "density", x = expression(Recovery~rate~(gamma)), y = "Duration") #, title="(B)")
#hh<- hh+ theme(axis.title = element_text(size=10), title=element_text(face="bold", size=10))
hh<- hh + theme(axis.text = element_text(vjust=0.5, size=6))
hh<- hh + theme(axis.text.x =element_text(vjust= 0, angle=-90))
hh<- hh + theme(axis.title = element_text(vjust=0.5, size=7))
hh<- hh + theme(plot.title = element_text(size=7)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=6)) 
hh<- hh + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
hh
#dev.off()

prow <- plot_grid(gg + theme(legend.position="none"),
            hh + theme(legend.position="none"),
           align = 'vh',
           labels = c("(A)", "(B)"),
           hjust = -1,
           ncol = 2, label_size=7
           )

tiff("Figure2.tiff", height = 7, width = 8.7, units = "cm", compression = "lzw", res = 1200)
prow
#multiplot(gg,hh, cols=2)
dev.off()

##Figure 3
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=6))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

jj<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", fill= expression(beta[2]))
jj<- jj+ theme(plot.title = element_text(size=7))
jj<- jj+ theme(axis.title = element_text(size=6))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
jj

prow <- plot_grid( ii + theme(legend.position="none"),
            jj + theme(legend.position="none"),
           align = 'vh',
           labels = c("(A)", "(B)"),
           hjust = -1,
           nrow = 2, label_size=7
           )

legend_b <- get_legend(ii + theme(legend.position="bottom"))

p <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .02))
p

tiff("Figure3test.tiff", height = 22.7, width = 17.8, units = "cm", compression = "lzw", res = 900)
#multiplot(ii,jj, cols=1)
p
dev.off()
```

##Figure 4
Comparing effects on landscape structure for select RSFs holding density, recovery rate and perceptual range constant.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

betas<-sub_data[which(sub_data$betas==c("3 0 0", "3 0 -1", "3 2 -0.5")),]
betas<-betas[which(betas$rec_rate==0.1 & betas$percep==3 & betas$density==0.5),]

#Individual plots of RSF box plot max prevalence and duration
ii<- ggplot(data=betas, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
ii<- ii+ geom_boxplot(stat="boxplot", position=position_dodge())
ii<- ii + facet_grid(betas ~.)
# ii<-ii +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
ii<- ii+ labs(x = "Landscape structure", y = "Maximum \n prevalence")
#ii<-ii +theme_grey()
#ii<-ii + theme(plot.title = element_text(hjust = 0.5))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
#ii <- ii+ theme(legend.position="none")
#ii<-ii+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
#ii<-ii+ theme(axis.ticks.x=element_blank())
#ii<-ii +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
ii

#Individual plots of RSF box plot max prevalence and duration
jj<- ggplot(data=betas, aes(x=lstructure, y=duration)) #, fill=covariation)
jj<- jj+ geom_boxplot(stat="boxplot", position=position_dodge())
jj<- jj + facet_grid(betas ~.)
# jj<-jj +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
jj<- jj+ labs(x = "Landscape structure", y = "Duration")
#jj<-jj +theme_grey()
#jj<-jj + theme(plot.title = element_text(hjust = 0.5))
jj<- jj+ theme(plot.title = element_text(size=7))
jj<- jj+ theme(axis.title = element_text(size=6))
jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
#jj <- jj+ theme(legend.position="none")
#jj<-jj+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
#jj<-jj+ theme(axis.ticks.x=element_blank())
#jj<-jj +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
jj

prow <- plot_grid(ii, jj,
           align = 'vh',
           labels = c("(A)", "(B)"),
           hjust = -1,
           ncol = 1, label_size=7
           )

tiff("Figure4.tiff", height = 12, width = 8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(ii,jj, cols=1)
prow
dev.off()

##Supplementary Figure S1
Box plot of percep vs. rec rate vs. density for every RSF combination
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data25<-sub_data[which(sub_data$density==0.25),]
sub_data50<-sub_data[which(sub_data$density==0.5),]

#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
gg<- ggplot(data=sub_data25, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
gg<-gg+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
gg<- gg+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(A)")
gg<- gg+ theme(axis.title = element_text(face="bold", size=20))
gg<- gg + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
gg<- gg + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
gg
#dev.off()

#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
hh<- ggplot(data=sub_data25, aes(x=betas, y=duration))#, fill=as.factor(density)))
#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
hh<-hh+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
hh<- hh+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=20))
hh<- hh + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14)) 
hh<- hh + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
hh
#dev.off()

#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
ii<- ggplot(data=sub_data50, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
ii<-ii+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
ii<- ii+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(C)")
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=14)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
ii
#dev.off()

#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
jj<- ggplot(data=sub_data50, aes(x=betas, y=duration))#, fill=as.factor(density)))
#jj<- jj+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
jj<-jj+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
jj<- jj+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(D)")
jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=14)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
jj

tiff("FigureS2.tiff", height = 20, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh,ii,jj, cols=1)
dev.off()

##Supplementary Figure S2 (Heat maps, density=0.25)
Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]

sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
gg <- gg + geom_tile(color="white", size=0.1)
gg <- gg + scale_fill_viridis(name="Duration")
gg <- gg + coord_equal()
gg <- gg + facet_grid(percep ~ betas)
gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
gg<- gg + theme(strip.text.x = element_text(angle = 90))
gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
gg

sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
hh <- hh + geom_tile(color="white", size=0.1)
hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
hh <- hh + coord_equal()
hh <- hh + facet_grid(percep ~ betas)
hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
hh<- hh + theme(strip.text.x = element_text(angle = 90))
hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
hh

r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.25),]
sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
ii <- ii + geom_tile(color="white", size=0.1)
ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
ii <- ii + coord_equal()
ii <- ii + facet_grid(percep ~ betas)
ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
ii<- ii + theme(strip.text.x = element_text(angle = 90))
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
ii

sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
jj <- jj + geom_tile(color="white", size=0.1)
jj <- jj + scale_fill_viridis(name="Duration")
jj <- jj + coord_equal()
jj <- jj + facet_grid(percep ~ betas)
jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
jj<- jj + theme(strip.text.x = element_text(angle = 90))
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
jj

r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.25),]
sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
kk <- kk + geom_tile(color="white", size=0.1)
kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
kk <- kk + coord_equal()
kk <- kk + facet_grid(percep ~ betas)
kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
kk<- kk + theme(strip.text.x = element_text(angle = 90))
kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
kk

sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
mm <- mm + geom_tile(color="white", size=0.1)
mm <- mm + scale_fill_viridis(name="Duration")
mm <- mm + coord_equal()
mm <- mm + facet_grid(percep ~ betas)
mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
mm<- mm + theme(strip.text.x = element_text(angle = 90))
mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
mm

tiff("FigureS4_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj,hh,gg, kk,mm, cols=1)
dev.off()
```

##Supplementary Figure S3 (Heat maps, density=0.5)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
gg <- gg + geom_tile(color="white", size=0.1)
gg <- gg + scale_fill_viridis(name="Duration")
gg <- gg + coord_equal()
gg <- gg + facet_grid(percep ~ betas)
gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
gg<- gg + theme(strip.text.x = element_text(angle = 90))
gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
gg

sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
hh <- hh + geom_tile(color="white", size=0.1)
hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
hh <- hh + coord_equal()
hh <- hh + facet_grid(percep ~ betas)
hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
hh<- hh + theme(strip.text.x = element_text(angle = 90))
hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
hh
